Meta-analysis

### 2019-11-05 04_Prep_data.Rmd
Created new cluster variable (spray_management) with six levels

slim_PM_dat %<>%
  mutate(
    cluster_1 = case_when(
      fungicide_timing_1 < 0 ~ "Early",
      fungicide_timing_1 >= 0 &
        fungicide_timing_1 < 4 ~ "Recommended",
      TRUE ~ "Late"
    )
  ) %>%
  mutate(
    cluster_2 = case_when(
      fungicide_timing_2 < 13 ~ "Early",
      fungicide_timing_2 >= 13 &
        fungicide_timing_2 < 17 ~ "Recommended",
      TRUE ~ "Late"
    )
  ) %>% 
  mutate(
    cluster_3 = case_when(
      fungicide_timing_3 < 14 ~ "Early",
      TRUE ~ "Recommended"
    )
  )

@@

>>>>

slim_PM_dat %<>%
  mutate(
    cluster_1 = case_when(
      fungicide_timing_1 < 0 ~ "Early",
      fungicide_timing_1 >= 0 &
        fungicide_timing_1 < 4 ~ "Recommended",
      TRUE ~ "Late"
    )
  ) %>%
  mutate(
    cluster_2 = case_when(
      is.na(fungicide_timing_2) ~ NA_character_,
      fungicide_timing_2 < 13 ~ "Early",
      fungicide_timing_2 >= 13 &
        fungicide_timing_2 < 17 ~ "Recommended",
      TRUE ~ "Late"
    )
  ) %>% 
  mutate(
    cluster_3 = case_when(
      fungicide_timing_3 < 14 ~ "Early",
      is.na(fungicide_timing_3) ~ NA_character_,
      TRUE ~ "Recommended"
    )
  )

@@

Cluster the clusters

```{r cluster_clusters}

clusters <- unique(slim_PM_dat[c("cluster_1","cluster_2","cluster_3")])

for(i in 1:nrow(clusters)){
   if(i == 1){clusters$n <- NA
   clusters$n_x_trial <- NA}

   clusters[i,"n"] <- nrow(slim_PM_dat[slim_PM_dat$cluster_1 == clusters[i,"cluster_1"] &
                                          slim_PM_dat$cluster_2 == clusters[i,"cluster_2"] &
                                          slim_PM_dat$cluster_3 == clusters[i,"cluster_3"],
                                       ])

   clusters[i,"n_x_trial"] <- length(unique(slim_PM_dat[slim_PM_dat$cluster_1 == clusters[i,"cluster_1"] &
                                          slim_PM_dat$cluster_2 == clusters[i,"cluster_2"] &
                                          slim_PM_dat$cluster_3 == clusters[i,"cluster_3"],
                                       "trial_ref"]))

knitr::kable(clusters)

From this we can see that there are 16 different cluster combinations, which would make the analysis too difficult. I will reduce this to 6 levels within one variable.

Single sprays either early, recommended timing or late.

Two sprays or more where the first spray was either early, recommended timing, or late.

```{r simple_clusters}

slim_PM_dat %>%
  mutate(
    spray_management = case_when(
       fungicide_timing_1 < 0 &
          is.na(fungicide_application_2) &
          is.na(fungicide_application_3) ~ "Early",
       fungicide_timing_1 >= 0 &
          fungicide_timing_1 < 4 &
          is.na(fungicide_application_2) &
          is.na(fungicide_application_3) ~ "Recommended",
      fungicide_timing_1 >= 4 &
          is.na(fungicide_application_2) &
          is.na(fungicide_application_3) ~ "Late",
      fungicide_timing_1 < 0 &
          !is.na(fungicide_application_2) ~ "Early_plus",
       fungicide_timing_1 >= 0 &
          fungicide_timing_1 < 4 &
          !is.na(fungicide_application_2) ~ "Recommended_plus",
      fungicide_timing_1 >= 4 &
          !is.na(fungicide_application_2) ~ "Late_plus",
      TRUE ~ NA_character_
    )
  )

slim_PM_dat[slim_PM_dat$fungicide_ai == "control",
            c("fungicide_timing_1", "fungicide_timing_2", "fungicide_timing_3",
              "spray_management"
              )] <- "control"

write.csv(slim_PM_dat, file = "data/slim_PM_clusterdat.csv", row.names = FALSE)
```
